Narrative

### 2023-05-23 manuscript/manuscript.qmd
methods: copyedits

The other effect size type we us is Pearson's $r$. Pearson's $r$ has the advantage that resulting heterogeneity estimates on this scale are more interpretable that on the Fisher $z$ scale. Although Fisher $z$ correlations can be back-transformed into Pearson's $r$ for interpretation, its heterogeneity cannot. A workaround is to compute a prediction interval and convert this interval onto the product-moment scale (Hedges & Vevea, 1998). The width of the interval can then be used as an estimate of the heterogeneity. We prefer to compute comparable heterogeneity values for Pearson's $r$ and Fisher's $z$ (see the methods section 'Parameter values') and report the bias in heterogeneity estimates, as we believe this is more interpretable for applied meta-analysts.

@@

We defined the between-studies standard deviation ($\tau$) to cover a wide range of variability in true effect sizes and empirical estimates reported in the psychological literature. Van Erp et al. (2017) provide empirical heterogeneity estimates from 747 meta-analyses in 61 article published in the journal Psychological Bulletin between 1990 - 2013. The median (uncorrected)Pearson's $r$ $\tau$ value in these data was 0.17 (interquartile range 0.1 - 0.24). The point of this study is that empirical heterogeneity estimates may not be accurately estimated. Nonetheless, we selected approximately the interquartile range of $\tau$-values reported in van Erp et al. for the product-moment correlation, both to make sure we covered the empirically reported range of values and because we considered them to represent reasonable variability on the product-moment correlation scale. The values we selected were {0, 0.1, 0.15, 0.2}. We selected the largest heterogeneity level to avoid excissive truncation for our maximum average effect size of 0.6: $\theta_i \sim N(\theta = 0.6, \tau = 0.2)$ implies approximately 95% of effect sizes will be below 1. Our values are similar to those used by Brannick et al. (2019) in their simulation study on the performance of different heterogeneity estimators after corrections for unreliability (they used $\tau = $ 0, 0.08, 0.13, 0.2).

>>>>

The other effect size type we use is Pearson's $r$. Pearson's $r$ has the advantage that resulting heterogeneity estimates on this scale are more interpretable than on the Fisher $z$ scale. Although Fisher $z$ correlations can be back-transformed into Pearson's $r$ for interpretation, its heterogeneity cannot. A workaround is to compute a prediction interval and convert this interval onto the product-moment scale (Hedges & Vevea, 1998). The width of the interval can then be used as an estimate of the heterogeneity. We prefer to compute comparable heterogeneity values for Pearson's $r$ and Fisher's $z$ (see the methods section 'Parameter values') and report the bias in heterogeneity estimates, as we believe this is more interpretable for applied meta-analysts.

@@

We defined the between-studies standard deviation ($\tau$) to cover a wide range of variability in true effect sizes and empirical estimates reported in the psychological literature. Van Erp et al. (2017) provide empirical heterogeneity estimates from 747 meta-analyses in 61 article published in the journal Psychological Bulletin between 1990 - 2013. The median (uncorrected)Pearson's $r$ $\tau$ value in these data was 0.17 (interquartile range 0.1 - 0.24). The point of this study is that empirical heterogeneity estimates may not be accurately estimated. Nonetheless, we selected approximately the interquartile range of $\tau$-values reported in van Erp et al. for the product-moment correlation, both to make sure we covered the empirically reported range of values and because we considered them to represent reasonable variability on the product-moment correlation scale. The values we selected were {0, 0.1, 0.15, 0.2}. We selected the largest heterogeneity level to avoid excessive truncation for our maximum average effect size of 0.6: $\theta_i \sim N(\theta = 0.6, \tau = 0.2)$ implies approximately 95% of effect sizes will be below 1. Our values are similar to those used by Brannick et al. (2019) in their simulation study on the performance of different heterogeneity estimators after corrections for unreliability (they used $\tau = $ 0, 0.08, 0.13, 0.2).
